DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-04 Draft Ped Metrics Example.Rmd
combined scores

comb_stand <- comb %>% 
  st_set_geometry(., NULL) %>% 
  mutate(setting = ifelse(RUCODE == 1, "Rural", 
                          ifelse(RUCODE == 2, "Urban", "Unknown")),
         ped_type = sub("\\:.*", "", TYPE),
         ped_w = as.numeric(sub(".*?([0-9]+).*", "\\1", TYPE)),
         nn = paste(sub("paved ","",tolower(ped_type)), tolower(SIDE_OF_RO),sep ="_")) %>%
  #select(RD_LOG_ID = RD_LOG_ID_R, SEGMENT_ID = SEGMENT_ID_R, FULL_NAME = FULL_NAME_R,
  #       SEGMENT_LENGTH = LENGTH_R, SW_SH_LENGTH = LENGTH, SIDE_OF_RO,
  #       distance, road_class, setting, nn, ped_w) %>%
  pivot_wider(id_cols = -SIDE_OF_RO, #c(RD_LOG_ID, SEGMENT_ID, FULL_NAME), 
              names_from = nn, 
              values_from = ped_w) %>%
  left_join(road_standards)

@@

ncdf_w_all_nogeo <- ncdf %>% #clean_roadcl %>%  
  st_set_geometry(., NULL) %>% 
  mutate(setting = ifelse(RUCODE == 1, "Rural", 
                          ifelse(RUCODE == 2, "Urban", "Unknown"))) %>%
  left_join(road_standards) %>%
  left_join(sw_sh) %>%
  mutate(score_left = getSideScore(standard_sidewalk, standard_shoulder, 
                                   sidewalk_left, shoulder_left),
         score_right = getSideScore(standard_sidewalk, standard_shoulder, 
                                   sidewalk_right, shoulder_right),
         score = score_left + score_right)

# ncdf %>% 
#   st_set_geometry(., NULL) %>% 
#   select(RD_LOG_ID, 
#          BMP = CRAB_BMP, 
#          EMP = CRAB_EMP,
#          LENGTH) %>%
#   left_join(select(st_set_geometry(shoulders_nc, NULL), RD_LOG_ID = ROAD_LOG_I, 
#                    BMP, EMP,
#                    SIDE_OF_RO, SHLDR_WIDT, SHLDR_SURF)) %>%
#   group_by(SHLDR_SURF, SHLDR_WIDT) %>%
#   summarise(n = n(), LENGTH = sum(LENGTH, na.rm = TRUE)/5280)
# 
# ncdf %>% 
#   st_set_geometry(., NULL) %>% 
#   select(RD_LOG_ID, FULL_NAME,
#          BMP = CRAB_BMP, 
#          EMP = CRAB_EMP,
#          LENGTH) %>%
#   left_join(select(mutate(st_set_geometry(sidewalks_nc, NULL), RD_LOG_ID = as.integer(ROADLOGID)), 
#                    RD_LOG_ID,
#                    BMP, EMP,
#                    SIDE_OF_RO, WIDTH)) %>%
#   filter(!is.na(WIDTH) & WIDTH > 0) %>%
#   group_by(RD_LOG_ID, FULL_NAME, `Sidewalk Width` = WIDTH) %>%
#   summarise(n = n(), LENGTH = sum(LENGTH, na.rm = TRUE)/5280)

knitr::kable(
 # ncdf_w_all_nogeo %>%
  comb_score %>%
  group_by(setting, road_class, score) %>% 
  summarise(roads = nice_comma(n_distinct(RD_LOG_ID_R)), 
            segments = nice_comma(n()), 
            length = nice_comma(sum(LENGTH, na.rm=TRUE)/5280, 1),
            dist = nice_comma(sum(distance, na.rm=TRUE)/5280, 1),
            .groups = "drop") 
  )
```

>>>>

comb_stand <- comb %>% 
  st_set_geometry(., NULL) %>% 
  mutate(setting = ifelse(RUCODE == 1, "Rural", 
                          ifelse(RUCODE == 2, "Urban", "Unknown")),
         ped_type = sub("\\:.*", "", TYPE),
         #ped_w = as.numeric(sub(".*?([0-9]+).*", "\\1", TYPE)),
         nn = paste(sub("paved ","",tolower(ped_type)), tolower(SIDE_OF_RO),sep ="_")) %>%
  #select(RD_LOG_ID = RD_LOG_ID_R, SEGMENT_ID = SEGMENT_ID_R, FULL_NAME = FULL_NAME_R,
  #       SEGMENT_LENGTH = LENGTH_R, SW_SH_LENGTH = LENGTH, SIDE_OF_RO,
  #       distance, road_class, setting, nn, ped_w) %>%
  pivot_wider(id_cols = c(-RD_LOG_ID:-TYPE,-ped_type), #c(RD_LOG_ID, SEGMENT_ID, FULL_NAME), 
              names_from = nn, 
              values_from = WIDTH,
              values_fn = mean) %>%
  left_join(road_standards)

@@

knitr::kable(
 # ncdf_w_all_nogeo %>%
  comb_score %>%
  group_by(setting, road_class, score) %>% 
  summarise(roads = nice_comma(n_distinct(RD_LOG_ID_R)), 
            segments = nice_comma(n()), 
            #length = nice_comma(sum(LENGTH, na.rm=TRUE)/5280, 1),
            dist = nice_comma(sum(distance, na.rm=TRUE)/5280, 1),
            .groups = "drop") 
  )
```
